---
title: "localEcozones Manual"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: false
editor_options:
  chunk_output_type: console
always_allow_html: true
---

```{r setup-localEcozones, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE, results = "hold")
```

# Overview

*localEcozones* makes LandR's `ecoregionLayer`, the polygons that *Biomass_borealDataPrep* uses
to estimate `establishprob`, `maxB` and `maxANPP` for each species. It uses the local
eco-zonation where one exists and national ecodistricts elsewhere. The BEC and Natural
Subregion options follow elevation, so valley and subalpine parameters are not mixed in one ecoregion:

- British Columbia: Biogeoclimatic Ecosystem Classification (BEC) zones, from the BC Data
  Catalogue (`bcLevel`: `"ZONE"`, `"SUBZONE"` or `"MAP_LABEL"`).
- Alberta: Natural Subregions of Alberta, 2005 (`abLevel`: `"NSRNAME"` or `"NRNAME"`). At the
  subregion level the Rocky Mountain region is split into Alpine, Subalpine and Montane.
- Elsewhere: the plain national ecodistrict. There are no elevation bands: zones shift with latitude, so a province-wide band is wrong.

On the South Coast of BC (ELF 13.2.2), western redcedar has more than 5% cover in 0.03% of the
pixels above 1,500 m. The share of its ecoregion that it covers, which drives its
`establishprob`, was 7.9% with ecodistricts and 0.4% with BEC zones.

The provincial layer defines its own extent; the province outline is only used to keep it out
of a neighbouring province. Labels are prefixed by province (`BC_CWH`, `AB_Subalpine`) or are
the ecodistrict and band (`ED1012_500-1000m`). They are in the fields `ecoregion` and
`ECODISTRIC`, the field *Biomass_borealDataPrep* reads by default.

To add a province, add a function to `localZonations()` in `R/localEcozones.R`.

# Parameters

```{r moduleParams, echo = FALSE, eval = TRUE, results = "asis"}
knitr::kable(SpaDES.core::moduleParams("localEcozones", ".."))
```

# Usage

List it before *Biomass_borealDataPrep*:

```{r usage}
modules = c("PredictiveEcology/localEcozones@main",
            "PredictiveEcology/Biomass_borealDataPrep@development", ...)
```
